Spatial Analysis

### 2021-06-15 Scripts/spatial_analisis.Rmd

---
title: "Spatial Analysis"
output: 
 # html_document
  html_notebook:
  fig_width: 6
  fig_height: 4
  toc: false
  toc_depth: 3
  code_folding: hide
  toc_float:
    collapsed: false
---

>>>>

---
title: "Spatial Analysis"
author: "Juliano Palacios Abrantes"
output:
  html_notebook:
    fig_width: 6
    fig_height: 4
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
    theme: darkly
---
